\section{Conclusions}
The following configuration was used for MiniZinc\graffito{MiniZinc solver configuration can be found in \path{src/minizinc/solver.mpc}.}:
\begin{description}
    \item[Solver: ] Chuffed 0.10.4
    \item[Number of solutions: ] All solutions
    \item[Optimization level: ] -O0 (no optimization)
    \item[Time limit: ] \SI{300}{s}
    \item[Annotations: ] \mintinline[breaklines]{minizinc}{int_search(Board, first_fail, indomain_median) satisfy;}
\end{description}

This set of choices was the result of a series of experiments on both small and large instances. As a result this was the combination of parameters that seems to perform better for this specific problem.


As we will see in section~\ref{sec:benchmarks} a set of 30 istances were created and solved. Keep in mind that not all results were manually checked for their correctness, only the ones with dimension of the Board equal to 3; however the equal number of solutions between ASP and MiniZinc of each instance was taken as a good indicator of the correctness of the models.

The order of magnitude of execution times is way below the one required, this is intended, as it was considered meaningless to go above a reasonable dimension of the board.

ASP is, as expected, considerably faster than MiniZinc, but not in all cases: when the number of solutions increases the difference between the two solvers decreases until MiniZinc seems to actually outperform ASP. 

It must be however noted that given the almost negligible deltas between execution times, most of the differences between the instances can be attributed to statistical fluctuation and/or different performance of the system at different times.

\section{Benchmarks}\label{sec:benchmarks}
\graffito{All the instances were randomly generated by the Python script.}You can find all the benchmark instances in the \path{src/minizinc/data} folder and \path{src/asp/data} folder. We briefly report an overview of the performance on the table below.

\vspace{3mm}

\begin{tabular}{|p{0.3cm}||p{1.6cm}|p{1.6cm}||p{1.6cm}|p{1.6cm}|p{1.6cm}| }
    \hline
    \multicolumn{6}{|c|}{Benchmark instances} \\
    \hline
    \# &Dimension &Starting points &Minizinc Time &ASP Time &Solutions\\
    \hline
    1 &3 &2 &\SI{506}{ms} &\SI{5}{ms} &4 \\
    2 &3 &2 &\SI{516}{ms} &\SI{16}{ms} &3 \\
    3 &3 &3 &\SI{367}{ms} &\SI{4}{ms} &1 \\
    4 &3 &3 &\SI{350}{ms} &\SI{8}{ms} &1 \\
    5 &3 &3 &\SI{369}{ms} &\SI{7}{ms} &1 \\
    \hline
    6 &4 &2 &\SI{363}{ms} &\SI{13}{ms} &3 \\
    7 &4 &2 &\SI{567}{ms} &\SI{105}{ms} &41 \\
    8 &4 &2 &\SI{566}{ms} &\SI{121}{ms} &35 \\
    9 &4 &3 &\SI{652}{ms} &\SI{20}{ms} &1 \\
    10 &4 &3 &\SI{626}{ms} &\SI{19}{ms} &4 \\
    11 &4 &3 &\SI{650}{ms} &\SI{20}{ms} &2 \\
    12 &4 &3 &\SI{599}{ms} &\SI{22}{ms} &3 \\
    13 &4 &4 &\SI{585}{ms} &\SI{27}{ms} &1 \\
    14 &4 &4 &\SI{565}{ms} &\SI{15}{ms} &1 \\
    15 &4 &4 &\SI{522}{ms} &\SI{13}{ms} &2 \\
    \hline
    16 &5 &2 &\SI{412}{ms} &\SI{185}{ms} &8 \\
    17 &5 &2 &\SI{774}{ms} &\SI{852}{ms} &66 \\
    18 &5 &2 &\SI{391}{ms} &\SI{89}{ms} &36 \\
    19 &5 &3 &\SI{425}{ms} &\SI{66}{ms} &9 \\
    20 &5 &3 &\SI{379}{ms} &\SI{31}{ms} &3 \\
    21 &5 &3 &\SI{715}{ms} &\SI{35}{ms} &2 \\
    22 &5 &3 &\SI{876}{ms} &\SI{96}{ms} &5 \\
    23 &5 &4 &\SI{707}{ms} &\SI{50}{ms} &1 \\
    24 &5 &4 &\SI{573}{ms} &\SI{41}{ms} &1 \\
    25 &5 &4 &\SI{554}{ms} &\SI{60}{ms} &1 \\
    \hline
    26 &6 &2 &\SI{897}{ms} &\SI{3483}{ms} &80 \\
    27 &6 &3 &\SI{810}{ms} &\SI{509}{ms} &15 \\
    28 &6 &3 &\SI{702}{ms} &\SI{193}{ms} &3 \\
    29 &6 &4 &\SI{840}{ms} &\SI{155}{ms} &2 \\
    30 &6 &4 &\SI{673}{ms} &\SI{141}{ms} &1 \\
    \hline
   \end{tabular}

   